---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FIHR

<!-- badges: start -->
<!-- badges: end -->

The goal of FIHR is to provide inference for linear and quadratic functionals in high-dimensional linear and logistic regression models. It computes bias-corrected estimators and corresponding standard errors for the linear and quadratic functionals.

## Installation

You can install the released version of FIHR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("FIHR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("prabrishar1/FIHR")
```
## Example

These are basic examples which show how to solve the common high-dimensional inference problems:

```{r example}
library(FIHR)
```

Inference for linear functional in high-dimensional linear regression model

```{r Linear Functional Linear Model}

library(MASS)
A1gen <- function(rho,p){
  A1=matrix(0,p,p)
  for(i in 1:p){
    for(j in 1:p){
      A1[i,j]<-rho^(abs(i-j))
    } 
  }
  A1
}
mu <- rep(0,400)
mu[1:5] <- c(1:5)/5
rho = 0.5
Cov <- (A1gen(rho,400))/2
beta <- rep(0,400)
beta[1:10] <- c(1:10)/5
X <- MASS::mvrnorm(100,mu,Cov)
y = X%*%beta + rnorm(100)
Est = FIHR::LF(X = X, y = y, loading = c(1,rep(0,399)), intercept = TRUE)
Est$prop.est
Est$se
```

Inference for linear functional in high-dimensional logistic regression model

```{r Linear Functional Logistic Model}
library(MASS)
A1gen <- function(rho,p){
  A1=matrix(0,p,p)
  for(i in 1:p){
    for(j in 1:p){
      A1[i,j]<-rho^(abs(i-j))
    } 
  }
  A1
}
mu <- rep(0,400)
rho = 0.5
Cov <- (A1gen(rho,400))/2
beta <- rep(0,400)
beta[1:10] <- c(1:10)/5
X <- MASS::mvrnorm(100,mu,Cov)
exp_val <- X%*%beta
prob <- exp(exp_val)/(1+exp(exp_val))
y <- rbinom(100,1,prob)
Est = FIHR::LF_logistic(X = X, y = y, loading = c(1,rep(0,399)), intercept = TRUE, weight = rep(1,100))
Est$prop.est
Est$se
```

Inference for quadratic functional in high-dimensional linear model

```{r Group Linear Model}
library(MASS)

A1gen <- function(rho,p){
  A1=matrix(0,p,p)
  for(i in 1:p){
    for(j in 1:p){
      A1[i,j]<-rho^(abs(i-j))
    } 
  }
  A1
}
rho = 0.6
Cov <- (A1gen(rho,400))
mu <- rep(0,400)
mu[1:5] <- c(1:5)/5
beta <- rep(0,400)
beta[25:50] <- 0.08
X <- MASS::mvrnorm(100,mu,Cov)
y <- X%*%beta + rnorm(100)
test.set <- c(30:100)

## Inference for Quadratic Functional with Population Covariance Matrix in middle

Est = FIHR::QF(X = X, y = y, test.set=test.set)
Est$prop.est
Est$se

## Inference for Quadratic Functional with known matrix A in middle

Est = FIHR::QF(X = X, y = y, test.set=test.set, A = diag(1:400,400),intercept = F)
Est$prop.est
Est$se

## Inference for square norm of regression vector

Est = FIHR::QF(X = X, y = y, test.set=test.set, A = diag(1,400),intercept = F)
Est$prop.est
Est$se
```
