---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SIHR

<!-- badges: start -->
<!-- badges: end -->

The goal of SIHR is to provide inference procedures in the high-dimensional setting for (1) linear functionals in generalized linear regression (GLM_LF), (2) quadratic functionals in linear regression (QF) (3) individual treatment effects in generalized linear regression (ITE).
## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("prabrishar1/SIHR")
```
## Example

These are basic examples which show how to solve the common high-dimensional inference problems:

```{r example}
library(SIHR)
```

### Inference for linear functional in high-dimensional linear regression model
Generate Data and find the truth linear functionals:
```{r Generate Data LF-linear}
set.seed(0)
X = matrix(rnorm(100*120), nrow=100, ncol=120)
y = -0.5 + X[,1] * 0.5 + X[,2] * 1 + rnorm(100)
loading.mat = cbind(c(1, 1, rep(0, 118)), c(-0.5, -1, rep(0, 118)))
## consider the intercept.loading 
truth1 = -0.5 + 0.5 * 1 + 1 * 1
truth2 = -0.5 + 0.5 * -0.5 + 1 * -1
truth = c(truth1, truth2)
truth
```

Call `LF` with `model="linear"`: 
```{r LF-linear}
Est = LF(X, y, loading.mat, model="linear", intercept.loading=TRUE, verbose=TRUE)
Est$est.plugin.vec ## plugin(biased) estimators
Est$est.debias.vec ## bias-corrected estimators
Est$se.vec ## standard errors for bias-corrected estimators
Est$ci.mat ## two-sided confidence interval for bias-corrected estimators
```

`summary` method for `LF`
```{r Summary LF-linear}
summary(Est)
```

