---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SIHR

<!-- badges: start -->
<!-- badges: end -->

The goal of SIHR is to provide inference procedures in the high-dimensional setting for (1) linear functionals in generalized linear regression, (2) individual treatment effects in generalized linear regression (ITE), (3) quadratic functionals in generalized linear regression (QF).

Currently, we support different generalized linear regression, by specifying the argument `model` in "linear", "logisitc", "logistic_alter" or "probit".

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("prabrishar1/SIHR")
```
## Examples

These are basic examples which show how to solve the common high-dimensional inference problems:

```{r example}
library(SIHR)
```

### Linear functional in linear regression model - 1
Generate Data and find the truth linear functionals:
```{r Generate Data LF-linear}
set.seed(0)
X = matrix(rnorm(100*120), nrow=100, ncol=120)
y = -0.5 + X[,1] * 0.5 + X[,2] * 1 + rnorm(100)
loading1 = c(1, 1, rep(0, 118))
loading2 = c(-0.5, -1, rep(0, 118))
loading.mat = cbind(loading1, loading2)
## consider the intercept.loading=FALSE
truth1 = 0.5 * 1 + 1 * 1
truth2 = 0.5 * -0.5 + 1 * -1
truth = c(truth1, truth2)
truth
```
In the example, the linear functional does not involve the intercept term, so we set `intercept.loading=FALSE` (default). If users want to include the intercept term, please set `intercept.loading=TRUE`, such that truth1 = -0.5 + 1.5 = 1; truth2 = -0.5 - 1.25 = -1.75

Call `LF` with `model="linear"`: 
```{r LF-linear}
Est = LF(X, y, loading.mat, model="linear", intercept=TRUE, intercept.loading=FALSE, verbose=TRUE)
```

`ci` method for `LF`
```{r ci LF-linear}
ci(Est)
```

`summary` method for `LF`
```{r Summary LF-linear}
summary(Est)
```

### Linear functional in linear regression model - 2

Sometimes, we may be interested in multiple linear functionals, each with a separate loading. To be computationally efficient, we can specify the argument `beta.init` first, so that the program can save time to compute the initial estimator repeatedly.
```{r Generate Data LF-linear-2}
set.seed(1)
X = matrix(rnorm(100*120), nrow=100, ncol=120)
y = -0.5 + X[,1:10] %*% rep(0.5, 10) + rnorm(100)
loading.mat = matrix(0, nrow=120, ncol=10)
for(i in 1:ncol(loading.mat)){
  loading.mat[i,i] =  1
}
```

```{r initial estimator LF-linear-2}
library(glmnet)
cvfit = cv.glmnet(X, y, family = "gaussian", alpha = 1, intercept = TRUE, standardize = T)
beta.init = as.vector(coef(cvfit, s = cvfit$lambda.min))
```
Call `LF` with `model="linear"`:
```{r LF-linear-2}
Est = LF(X, y, loading.mat, model="linear", intercept=TRUE, beta.init=beta.init, verbose=TRUE)
```

`ci` method for `LF`
```{r ci LF-linear-2}
ci(Est)
```

`summary` method for `LF`
```{r Summary LF-linear-2}
summary(Est)
```


### Linear functional in logistic regression model
Generate Data and find the truth linear functionals:
```{r Generate Data LF-logistic}
set.seed(0)
X = matrix(rnorm(100*120), nrow=100, ncol=120)
exp_val = -0.5 + X[,1] * 0.5 + X[,2] * 1
prob = exp(exp_val) / (1+exp(exp_val))
y = rbinom(100, 1, prob)
## loadings
loading1 = c(1, 1, rep(0, 118))
loading2 = c(-0.5, -1, rep(0, 118))
loading.mat = cbind(loading1, loading2)
## consider the intercept.loading=TRUE
truth1 = 0.5 * 1 + 1 * 1
truth2 = 0.5 * -0.5 + 1 * -1
truth = c(truth1, truth2)
truth.prob = exp(truth) / (1 + exp(truth))
truth; truth.prob
```

Call `LF` with `model="logistic"` or `model="logistic_alter"`: 
```{r LF-logistic}
## model = "logisitc"
Est = LF(X, y, loading.mat, model="logistic", verbose=TRUE)
```

`ci` method for `LF`
```{r ci LF-logistic}
## confidence interval for linear combination
ci(Est)
## confidence interval after probability transformation
ci(Est, probability = TRUE)
```

`summary` method for `LF`
```{r Summary LF-logistic}
summary(Est)
```

Call `LF` with `model="logistic_alter"`: 
```{r LF-logistic-alter}
## model = "logistic_alter"
Est = LF(X, y, loading.mat, model="logistic_alter", verbose=TRUE)
```

`ci` method for `LF`
```{r ci LF-logistic-alter}
## confidence interval for linear combination
ci(Est)
## confidence interval after probability transformation
ci(Est, probability = TRUE)
```

`summary` method for `LF`
```{r Summary LF-logistic-alter}
summary(Est)
```

### Individualized Treatment Effect in linear regression model
Generate Data and find the truth linear functionals:
```{r Generate Data ITE-linear}
set.seed(0)
## 1st data
X1 = matrix(rnorm(100*120), nrow=100, ncol=120)
y1 = -0.5 + X1[,1] * 0.5 + X1[,2] * 1 + rnorm(100)
## 2nd data
X2 = matrix(0.8*rnorm(100*120), nrow=100, ncol=120)
y2 = 0.1 + X2[,1] * 0.8 + X2[,2] * 0.8 + rnorm(100)
## loadings
loading1 = c(1, 1, rep(0, 118))
loading2 = c(-0.5, -1, rep(0, 118))
loading.mat = cbind(loading1, loading2)
truth1 = (0.5*1 + 1*1) - (0.8*1 + 0.8*1)
truth2 = (0.5*(-0.5) + 1*(-1)) - (0.8*(-0.5) + 0.8*(-1))
truth = c(truth1, truth2)
truth
```

Call `ITE` with `model="linear"`:
```{r ITE-linear}
Est = ITE(X1, y1, X2, y2, loading.mat, model="linear", verbose=TRUE)
```

`ci` method for `ITE`
```{r ci ITE-linear}
ci(Est)
```

`summary` method for `ITE`
```{r Summary ITE-linear}
summary(Est)
```

### Individualized Treatment Effect in logistic regression model
Generate Data and find the truth linear functionals:
```{r Generate Data ITE-logistic}
set.seed(0)
## 1st data
X1 = matrix(rnorm(100*120), nrow=100, ncol=120)
exp_val1 = -0.5 + X1[,1] * 0.5 + X1[,2] * 1
prob1 = exp(exp_val1) / (1 + exp(exp_val1))
y1 = rbinom(100, 1, prob1)
## 2nd data
X2 = matrix(0.8*rnorm(100*120), nrow=100, ncol=120)
exp_val2 = -0.5 + X2[,1] * 0.8 + X2[,2] * 0.8
prob2 = exp(exp_val2) / (1 + exp(exp_val2))
y2 = rbinom(100, 1, prob2)
## loadings
loading1 = c(1, 1, rep(0, 118))
loading2 = c(-0.5, -1, rep(0, 118))
loading.mat = cbind(loading1, loading2)
truth1 = (0.5*1 + 1*1) - (0.8*1 + 0.8*1)
truth2 = (0.5*(-0.5) + 1*(-1)) - (0.8*(-0.5) + 0.8*(-1))
truth = c(truth1, truth2)
prob.fun = function(x) exp(x)/(1+exp(x))
truth.prob1 = prob.fun(0.5*1 + 1*1) - prob.fun(0.8*1 + 0.8*1)
truth.prob2 = prob.fun(0.5*(-0.5) + 1*(-1)) - prob.fun(0.8*(-0.5) + 0.8*(-1))
truth.prob = c(truth.prob1, truth.prob2)

truth; truth.prob
```

Call `ITE` with `model="logistic"` or `model="logisitc_alter"`:
```{r ITE-logisitc}
Est = ITE(X1, y1, X2, y2, loading.mat, model="logistic", verbose = TRUE)
```

`ci` method for `ITE`:
```{r ci ITE-logistic}
## confidence interval for linear combination
ci(Est)
## confidence interval after probability transformation
ci(Est, probability = TRUE)
```

`summary` method for `ITE`:
```{r summary ITE-logistic}
summary(Est)
```


### Quadratic functional in linear regression
Generate Data and find the truth quadratic functionals:
```{r Generate Data QF-linear}
set.seed(0)
A1gen <- function(rho, p){
  M = matrix(NA, nrow=p, ncol=p)
  for(i in 1:p) for(j in 1:p) M[i,j] = rho^{abs(i-j)}
  M
}
Cov = A1gen(0.5, 150)
X = MASS::mvrnorm(n=200, mu=rep(0, 150), Sigma=Cov)
beta = rep(0, 150); beta[25:50] = 0.2
y = X%*%beta + rnorm(200)
test.set = c(40:60)
truth = as.numeric(t(beta[test.set])%*%Cov[test.set, test.set]%*%beta[test.set])
truth
```

Call `QF` with `model="linear"`:
```{r QF-linear}
tau1 = c(0.5, 1)
tau2 = 0
Est = QF(X, y, G=test.set, A=NULL, model="linear", tau1=tau1, tau2=tau2, verbose=TRUE)
```

`ci` method for `QF`
```{r ci QF-linear}
ci(Est)
```

`summary` method for `QF`
```{r Summary QF-linear}
summary(Est)
```

### Quadratic functional in logistic regression
Generate Data and find the truth quadratic functional
```{r Generate Data QF-logistic}
set.seed(0)
A1gen <- function(rho, p){
  M = matrix(NA, nrow=p, ncol=p)
  for(i in 1:p) for(j in 1:p) M[i,j] = rho^{abs(i-j)}
  M
}
Cov = A1gen(0.5, 150)
X = MASS::mvrnorm(n=200, mu=rep(0, 150), Sigma=Cov)
beta = rep(0, 150); beta[25:50] = 0.2
exp_val = X%*%beta
prob = exp(exp_val) / (1+exp(exp_val))
y = rbinom(200, 1, prob)
test.set = c(40:60)
truth = as.numeric(t(beta[test.set]%*%Cov[test.set, test.set]%*%beta[test.set]))
truth
```

Call `QF` with `model="logistic"` or `model="logisitc"`:
```{r QF-logisitc}
tau1 = c(0.5, 1)
tau2 = 0
Est = QF(X, y, G=test.set, A=NULL, model="logistic", tau1=tau1, tau2=tau2, verbose=TRUE)
```

`ci` method for `QF`:
```{r ci QF-logistic}
ci(Est)
```

`summary` method for `QF`:
```{r summary QF-logistic}
summary(Est)
```

Call `QF` with `model="logisitc"`:
```{r QF-logisitc-alter}
tau1 = c(0.5, 1)
tau2 = 0
Est = QF(X, y, G=test.set, A=NULL, model="logistic_alter", tau1=tau1, tau2=tau2, verbose=TRUE)
```

`ci` method for `QF`:
```{r ci QF-logistic-alter}
ci(Est)
```

`summary` method for `QF`:
```{r summary QF-logistic-alter}
summary(Est)
```
